Effect of multiple reflection of the sky signal off the HERA element on the measurements of 21cm power spectrum

### 2015-11-03 DishReflectometry/Paper1_v0.tex
Added 2 paragraphs to intro

\author{Zaki Ali\altaffilmark{1}, Carina Cheng\altaffilmark{1}, Dave DeBoer\altaffilmark{1}}
\author{Gilbert Hsyu\altaffilmark{2}, Tsz Kuk Leung\altaffilmark{2}, Aaron Parsons\altaffilmark{1}}

@@

\section{Introduction}
The efficacy of the techniques of foreground removal from the measured data critically limits the 21~cm power spectrum measurements. The delay transformation technique of foreground removal, introduced by  \citep{ParsonsBacker2009,Parsons2012} computes the Fourier transform of the visibility measured by an interferometer and produces a spectrum, referred to as delay spectrum hereafter, which is a function of the geometric time delay corresponding to the physical length of the baseline between two antennas. For the visibilities measured over a wide field across wide frequency bandwidth, the delay spectrum is constituted by the instrument response, the foreground signal and 21cm power spectrum, hereafter referred to as EoR signal.
%The complex visibility measured by an interferometer is a convolution of the instrument response with the true sky response in the UV plane. Therefore, when Fourier transformed, the delay spectrum is the multiplication of the sky response with the instrument response in the delay domain.
The technique exploits the smooth spectral characteristics of the foreground and for a widefield wide bandwidth visibility measurement by an interferometer with a baseline $b$, confines the foreground contribution to the computed delay spectrum within the largest possible time delay $\tau = b/c$ corresponding to the given baseline length. Such techniques also assumes a spectrally smooth instrumental response whose contribution to the measured data, much as the contribution of the smooth spectrum foreground, also has an upper bound in the delay space imposed by the largest geometric delay of the given baseline. 
Beyond this limit, for an ideal system performance, the delay spectrum would be dominated by any wideband signal across the sky with spectral and spatial fluctuation over small scale such as the EoR signal and therefore, could be detectable.\\ 
The interaction between the sky signal and instrument response can alter the relative contribution of the foreground, instrument response and the EoR signal at a given delay and thus influence the detectability of the EoR signal. Such interactions may cause the foreground and systematics to spill over at higher delays and thus push the upper limit of the foreground and systematic contaminated delay modes to much higher delays. In this process, the EoR signal over large spatial scale will be lost.

>>>>

\author{Zaki Ali\altaffilmark{1}, Carina Cheng\altaffilmark{1}, Dave DeBoer\altaffilmark{1}}
\author{Gilbert Hsyu\altaffilmark{2}, Tsz Kuk Leung\altaffilmark{2}, Aaron Parsons\altaffilmark{1}}
% XXX add all members of HERA collaboration
% XXX suggest Patra, Parsons, Ali, DeBoer, Cheng, Leung, Hsyu, alphabetical

@@

\section{Introduction}

Since it was first proposed in \citet{shaver_et_al1999}, measuring 21~cm
emission from neutral hydrogen in our early universe has gained attention as a
powerful probe of both cosmology and astrophysics.  While the science case for
21~cm cosmology, particularly during the Epoch of Reionization, is well
established (see, e.g.,
\citealt{furlanetto_et_al2006,morales_wyithe2010,furlanetto_loeb2014,pritchard_loeb2014}),
the technical path toward measuring this signal has been more problematic.  The
weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
cosmological history, but it also creates sensitivity and calibration
challenges that have yet to be fully solved.  With noise temperatures dominated
by sky noise \citep{XXX} and foregrounds four to five orders of magnitude
brighter than the signal \citep{XXX}, 21~cm reionization experiments must
furnish both collecting area and foreground suppression at levels significantly
beyond anything previously achieved in radio telescopes operating below 1 GHz.

One of the most problematic effects facing these experiments results form instrument
chromaticity.  The spectral dimension of 21~cm reionization experiments is of vital
importance; for line emission, this coordinate translates to a line-of-sight distance
that can be used to construct three-dimensional maps (and power spectra) of emission,
as well as probe the evolution of 21~cm emission over cosmological timescales.
The evolving response of a radio telescope --- either a single dish
or an interferometer --- versus spectral frequency modulates spectrally smooth foregrounds ,
contaminating spectral modes that might
otherwise be used to measure reionization \citep{XXX}.  Moreover, the chromaticity of
a telescope's response pattern scales linearly with diameter, putting the
needs of foreground suppression and signal sensitivity in direct tension with one
another.

% XXX the wedge

The efficacy of the techniques of foreground removal from the measured data critically limits the 21~cm power spectrum measurements. The delay transformation technique of foreground removal, introduced by  \citep{ParsonsBacker2009,Parsons2012} computes the Fourier transform of the visibility measured by an interferometer and produces a spectrum, referred to as delay spectrum hereafter, which is a function of the geometric time delay corresponding to the physical length of the baseline between two antennas. For the visibilities measured over a wide field across wide frequency bandwidth, the delay spectrum is constituted by the instrument response, the foreground signal and 21cm power spectrum, hereafter referred to as EoR signal.
%The complex visibility measured by an interferometer is a convolution of the instrument response with the true sky response in the UV plane. Therefore, when Fourier transformed, the delay spectrum is the multiplication of the sky response with the instrument response in the delay domain.
The technique exploits the smooth spectral characteristics of the foreground and for a widefield wide bandwidth visibility measurement by an interferometer with a baseline $b$, confines the foreground contribution to the computed delay spectrum within the largest possible time delay $\tau = b/c$ corresponding to the given baseline length. Such techniques also assumes a spectrally smooth instrumental response whose contribution to the measured data, much as the contribution of the smooth spectrum foreground, also has an upper bound in the delay space imposed by the largest geometric delay of the given baseline. 
Beyond this limit, for an ideal system performance, the delay spectrum would be dominated by any wideband signal across the sky with spectral and spatial fluctuation over small scale such as the EoR signal and therefore, could be detectable.\\ 
The interaction between the sky signal and instrument response can alter the relative contribution of the foreground, instrument response and the EoR signal at a given delay and thus influence the detectability of the EoR signal. Such interactions may cause the foreground and systematics to spill over at higher delays and thus push the upper limit of the foreground and systematic contaminated delay modes to much higher delays. In this process, the EoR signal over large spatial scale will be lost.
